A Decentralized Pub/Sub System for Trusted Machine Economy

### 2020-05-13 paper.tex
Modify Background smart contract

\section{Background}
In this section, we review the architecture of decentralized data marketplace and the two key components, Ethereum Smart Contract and MAM.

\subsection{Participants in Decentralized Data Marketplace}
There are three major roles, data providers, data consumers and brokers in the decentralized data marketplace which is similar to the pub/sub messaging model. But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others, in our proposed architecture, the brokers are only responsible for message delivery and essential verification processes. Fig.~\ref{fig:system_design}

\begin{itemize}
\item \textbf{Data Provider: }
Data providers can either generate, filter ,or process streaming data. The price of data products can They can make use of subscription fee that earned via trading for maintaining the equipment and improving the quality of data.
\item \textbf{Data Consumer: }
Data consumers are entities that are willing to buy data streams or high quality data sets. As data streams can be used in various applications and researches, it is hard to collect data from scratch. Thus, purchase is the fastest way to reach the goal. 
\item \textbf{Broker: }
Brokers are responsible for building agreement between data providers and consumers. Also brokers can represent data providers to perform computing tasks as brokers are expected to have higher resource. 
\end{itemize}

\subsection{Ethereum Smart Contract}
Ethereum is a cryptocurrency building on top of a public blockchain-based distributed ledger. It also provides a decentralized virtual machine that can perform the smart contract which is written by turing complete scripting
language.

The smart contract is a protocol for formulating agreement on a blockchain that provides verification and execution of the contract. The code in the smart contract can interact with other contracts, make decisions, store data and transfer cryptocurrency. All conditions and states established in the contract are transparent and enforceable. The appearance of smart contracts makes trading more flexible, and achieves more complex trading patterns in reality.

% to be removed
The Product Contract is used during the trading process, where Product Contract records all the details of data products, such as MAM channel's and endpoint's ID, blinded session key and data providers' DID Document address. Furthermore, data providers and subscribers exchange session keys through a Product Contract without involving brokers. Though this design may cost more in transaction fees than doing so off-chain, it is considered a better strategy to assure the profit of both providers and subscribers. The further details of key exchangement will be illustrated in Section~\ref{section:trading}.

>>>>

\section{Background}
In this section, we review the architecture of decentralized data marketplace and the two key components in the system, Ethereum Smart Contract and MAM.

\subsection{Participants in Decentralized Data Marketplace}
There are three major roles, data providers, data consumers and brokers in the decentralized data marketplace which is similar to the pub/sub messaging model. But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others. In our proposed architecture, the brokers are only responsible for message delivery and essential verification processes. Fig.~\ref{fig:system_design}

\begin{itemize}
\item \textbf{Data Provider: }
Data providers are the ones that generate, or filter streaming data, and set the data price based on the different types of data. With the subscription fee that earned via trading, data providers are incentivized to maintain and improve the quality of data.
\item \textbf{Data Consumer: }
Data consumers are entities that are willing to buy data streams. As it is laborious to widely deploy devices to collect data from scratch, and without a marketplace, it is also difficult to find providers of the data sets, purchases is the fastet and efficient way to get the desired data sets. 
\item \textbf{Broker: }
Brokers are responsible for building an agreement between data providers and consumers. Also brokers can represent data providers to perform computing tasks as brokers are expected to have higher resource. 
\end{itemize}

\subsection{Ethereum Smart Contract}
Ethereum is a cryptocurrency building on top of a public blockchain-based distributed ledger. 
It provides the smart contract, which is a protocol for formulating agreement on a blockchain that running on decentralized virtual machines. A smart contract can interact with other contracts, make decisions, store data and transfer cryptocurrency. All the participants in Ethereum can verify and execute the contracts, and once the contract is triggered, it will be executed automatically without any third-parties and it is uninterruptible.

With the functionalities of Ethereum smart contracts, a flexible and verifiable trading mechanism can be acheived. \textbf{Product Contract} is made for the product launching and trading process in the decentralized data marketplace. The information of data products such as MAM channel ID (the data entry point), data price, time period and the broker-verified encryption key are listed on Product Contract. Furthermore, the participants can exchange encryption keys without any authorities via smart contracts. Though this design may cost extra transaction fees than exchanging key off-chain, it is considered a more secure strategy to protect the privacy of both providers and subscribers.
